Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-08 manuscript/manuscript.Rmd
adjusted figure 2 caption and abstract

abstract: | 
  For any scientific report, repeating the original analyses upon the original data should yield the original outcomes. We evaluated analytic reproducibility in `r knitr::load_cache(label = 'abstract_text', object = 'totalArticles')` Psychological Science articles awarded open data badges between 2014-2015. Initially, `r knitr::load_cache(label = 'abstract_text', object = 'intialReproRateArticles')` articles contained at least one “major numerical discrepancy” (>10% difference) prompting us to request input from original authors. Ultimately, target values were reproducible without author involvement for `r knitr::load_cache(label = 'abstract_text', object = 'repro_noAI')` articles; reproducible with author involvement for `r knitr::load_cache(label = 'abstract_text', object = 'repro_withAI')` articles; not fully reproducible with no substantive author response for `r knitr::load_cache(label = 'abstract_text', object = 'noRepro_noAI')` articles; and not fully reproducible despite author involvement for `r knitr::load_cache(label = 'abstract_text', object = 'noRepro_withAI')` articles. Overall, `r knitr::load_cache(label = 'abstract_text', object = 'majorErrors')` major numerical discrepancies remained out of `r knitr::load_cache(label = 'abstract_text', object = 'totalValues')` checked values `r knitr::load_cache(label = 'abstract_text', object = 'reproRateValues')`, but original conclusions did not appear affected. Non-reproducibility was primarily caused by unclear analysis reporting. These results highlight that open data alone is not sufficient to ensure analytic reproducibility.

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of original p-values, classified by reproducibility outcome. Axes are on a log scale. Dashed lines represent the typical 0.05 threshold for statistical significance. For display purposes, 41 values below 0.001 are not shown.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```
```{r}
source(here('analysis','meta_analysis.R'))
```

>>>>

abstract: | 
  For any scientific report, repeating the original analyses upon the original data should yield the original outcomes. We evaluated analytic reproducibility in `r knitr::load_cache(label = 'abstract_text', object = 'totalArticles')` Psychological Science articles awarded open data badges between 2014-2015. Initially, `r knitr::load_cache(label = 'abstract_text', object = 'intialReproRateArticles')` articles contained at least one “major numerical discrepancy” (>10% difference) prompting us to request input from original authors. Ultimately, target values were reproducible without author involvement for `r knitr::load_cache(label = 'abstract_text', object = 'repro_noAI')` articles; reproducible with author involvement for `r knitr::load_cache(label = 'abstract_text', object = 'repro_withAI')` articles; not fully reproducible with no substantive author response for `r knitr::load_cache(label = 'abstract_text', object = 'noRepro_noAI')` articles; and not fully reproducible despite author involvement for `r knitr::load_cache(label = 'abstract_text', object = 'noRepro_withAI')` articles. Overall, `r knitr::load_cache(label = 'abstract_text', object = 'majorErrors')` major numerical discrepancies remained out of `r knitr::load_cache(label = 'abstract_text', object = 'totalValues')` checked values `r knitr::load_cache(label = 'abstract_text', object = 'reproRateValues')`, but original conclusions did not appear affected. Non-reproducibility was primarily caused by unclear reporting of analytic procedures. These results highlight that open data alone is not sufficient to ensure analytic reproducibility.

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of original p-values, classified by reproducibility outcome. Axes are on a log scale. Dashed lines represent the typical 0.05 threshold for statistical significance. For display purposes, 41 values below 0.001 are not shown. Original values reported as thresholds (e.g., p < .05) are represented by the threshold value when there was a major discrepancy and represented by the reanalysis value when there was a match.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```

```{r}
source(here('analysis','meta_analysis.R'))
```
